---
title: "Setup and Play with Quantstrat"
output:
  html_document: default
  pdf_document: default
---

Based on the Course [Financial Trading in R](https://learn.datacamp.com/courses/financial-trading-in-r)

# Setup

```{r setup, include=FALSE}
pacman::p_load(remotes, devtools)
#remotes::install_github("braverock/blotter")
#remotes::install_github("braverock/quantstrat")
pacman::p_load(quantmod, quantstrat, TTR)
```

## Two trading philosophies

-   Trend trading (also divergence or momentum), which is a bet that a quantity, such as a price, will keep moving in its current direction.
-   Reversion trading (also convergence, cycle, or oscillation), which is a bet that a quantity, such as a price, will reverse.

## How to prevent overfitting

-   Examining the robustness of system performance.
-   Reducing the number of parameters in the trading system.
-   Conducting tests to determine statistical significance of a strategy.

# Getting Bitcoin data

```{r}
# Get Bitcoin price from yahoo
getSymbols("BTC-USD",
           from = "2015-01-01", 
           to = "2020-12-31", 
           src = "yahoo", 
           adjust =  TRUE)

BTC_USD <- na.exclude(`BTC-USD`, 0)

# Plot the closing price of BTC
plot(Cl(BTC_USD))

# Adding moving average
lines(SMA(Cl(BTC_USD), n = 200), col = "red")
```

# Setting up a Strategy

### Understanding initialization settings

Let's get started with creating our first strategy in `quantstrat`. In this exercise, you will need to fill in three dates:

1.  An initialization date for your backtest.

2.  The start of your data.

3.  The end of your data.

```{r}
# Load the quantstrat package
library(quantstrat)

# Create initdate, from, and to strings
initdate <- "1999-01-01"
from <- "2000-01-01"
to <- "2021-02-28"

# Set the timezone to UTC
Sys.setenv(TZ = "UTC")

# Set the currency to USD 
currency("USD")
```

Let's continue the setup of your strategy. First, you will set a trade size of 100,000 USD in an object called `tradesize` which determines the amount you wager on each trade. Second, you will set your initial equity to 100,000 USD in an object called `initeq`.

Quantstrat requires three different objects to work: an **account**, a **portfolio**, and a **strategy**. An account is comprised of portfolios, and a portfolio is comprised of strategies. For your first strategy, there will only be one account, one portfolio, and one strategy. Let's call them `"firststrat"` for "first strategy".

Finally, before proceeding, you must remove any existing strategies using the strategy removal command `rm.strat()` which takes in a string of the name of a strategy.

```{r}
# Define your trade size and initial equity
tradesize <- 100000
initeq <- 100000

# Define the names of your strategy, portfolio and account
strategy.st <- "firststrat"
portfolio.st <- "firststrat"
account.st <- "firststrat"

# Remove the existing strategy if it exists
rm.strat(strategy.st)
```

Now that everything has been named, you must initialize the portfolio, the account, the **orders**, and the strategy to produce results.

-   The portfolio initialization `initPortf()` needs a portfolio string `name`, a vector for `symbols` used in the backtest, an initialization date `initDate`, and a `currency`.

-   The account initialization call `initAcct()` is identical to the portfolio initialization call except it takes an account string `name` instead of a new portfolio name, an existing `portfolios` name, and an initial equity `initEq`.

-   The orders initialization `initOrders()` needs a portfolio string `portfolio` and an initialization date `initDate`.

-   The strategy initialization `strategy()` needs a `name` of this new strategy and must have `store` set to `TRUE`.

```{r}
# Initialize the portfolio
initPortf(portfolio.st, symbols = "BTC-USD", initDate = initdate, currency = "USD")

# Initialize the account
initAcct(account.st, portfolios = portfolio.st, initDate = initdate, currency = "USD", initEq = initeq)

# Initialize the orders
initOrders(portfolio.st, initDate = initdate)

# Store the strategy
strategy(strategy.st, store = TRUE)
```

# Indicators

Indicators are crucial for your trading strategy. They are transformations of market data that allow a clearer understanding of its overall behavior, usually in exchange for lagging the market behavior. Here, you will be working with both trend types of indicators as well as oscillation indicators. You will also learn how to use pre-programmed indicators available in other libraries as well as implement one of your own.

The SMA and RSI functions

The **simple moving average (SMA)** and **relative strength index (RSI)** are two classic indicators. As you saw in Chapter 1, the SMA is an arithmetic moving average of past prices, while the RSI is a bounded oscillating indicator that ranges from 0 to 100. Their respective functions `SMA()` and `RSI()` both take in a series of prices, denoted by `x` and `price` respectively, and a lookback period `n`, for example:

```{r}
# Create a 200-day SMA
spy_sma <- SMA(x = Cl(BTC_USD), n = 200)

# Create an RSI with a 3-day lookback period
spy_rsi <- RSI(price = Cl(BTC_USD), n = 3)
```

```{r}
# Plot the closing prices of BTC_USD
plot(Cl(BTC_USD))

# Overlay a 200-day SMA
lines(SMA(Cl(BTC_USD), n = 200), col = "red")

# What kind of indicator?
# trend
```

The [Relative Strength Index (RSI)](http://www.investopedia.com/terms/r/rsi.asp) is another indicator that rises with positive price changes and falls with negative price changes. It is equal to 100 - 100/(1 + RS), where RS is the average gain over average loss over the lookback period. At various lengths, this indicator can range from a reversion indicator, to a trend filter, or anywhere in between. There are various ways of computing the RSI.

```{r}
# Plot the closing price of BTC_USD
plot(Cl(BTC_USD))

# Plot the RSI 2
plot(RSI(Cl(BTC_USD), n = 2))

# What kind of indicator?
# print("reversion")
```

# Adding an Indicator

```{r}
# Add a 200-day SMA indicator to strategy.st
add.indicator(strategy = strategy.st, 
              
              # Add the SMA function
              name = "SMA", 
              
              # Create a lookback period
              arguments = list(x = quote(Cl(BTC_USD)), n = 200), 
              
              # Label your indicator SMA200
              label = "SMA200")
```

```{r}
# Add a 50-day SMA indicator to strategy.st
add.indicator(strategy = strategy.st, 
              
              # Add the SMA function
              name = "SMA", 
              
              # Create a lookback period
              arguments = list(x = quote(Cl(BTC_USD)), n = 50), 
              
              # Label your indicator SMA50
              label = "SMA50")
```

```{r}
# Add an RSI 3 indicator to strategy.st
add.indicator(strategy = strategy.st, 
              
              # Add the RSI 3 function
              name = "RSI", 
              
              # Create a lookback period
              arguments = list(price = quote(Cl(BTC_USD)), n = 3), 
              
              # Label your indicator RSI_3
              label = "RSI_3")
```

# Writing our own Indicators

```{r}
# Write the calc_RSI_avg function
calc_RSI_avg <- function(price, n1, n2) {
  
  # RSI 1 takes an input of the price and n1
  RSI_1 <- RSI(price = price, n = n1)
  
  # RSI 2 takes an input of the price and n2
  RSI_2 <- RSI(price = price, n = n2)
  
  # RSI_avg is the average of RSI_1 and RSI_2
  RSI_avg <- (RSI_1 + RSI_2)/2
  
  # Your output of RSI_avg needs a column name of RSI_avg
  colnames(RSI_avg) <- "RSI_avg"
  return(RSI_avg)
}

# Add this function as RSI_3_4 to your strategy with n1 = 3 and n2 = 4
add.indicator(strategy.st, name = "calc_RSI_avg", arguments = list(price = quote(Cl(BTC_USD)), n1 = 3, n2 = 4), label = "RSI_3_4")
```

While the RSI is decent, it is somewhat outdated as far as indicators go. In this exercise, you will code a simplified version of another indicator from scratch. The indicator is called the **David Varadi Oscillator (DVO)**, originated by David Varadi, a quantitative research director.

The purpose of this oscillator is similar to something like the RSI in that it attempts to find opportunities to buy a temporary dip and sell in a temporary uptrend. In addition to obligatory market data, an oscillator function takes in two lookback periods.

First, the function computes a ratio between the closing price and average of high and low prices. Next, it applies an SMA to that quantity to smooth out noise, usually on a very small time frame, such as two days. Finally, it uses the [runPercentRank()](http://www.rdocumentation.org/packages/TTR/versions/0.23-1/topics/runPercentRank) function to take a running percentage rank of this average ratio, and multiplies it by 100 to convert it to a 0-100 quantity.

Think about the way that students get percentile scores after taking a standardized test (that is, if a student got an 800 on her math section, she might be in the 95th percentile nationally). `runPercentRank()` does the same thing, except over time. This indicator provides the rank for the latest observation when taken in the context over some past period that the user specifies. For example, if something has a runPercentRank value of .90 when using a lookback period of 126, it means it's in the 90th percentile when compared to itself and the past 125 observations.

Your job is to implement this indicator and save it as `DVO`. Some of the necessary code has been provided, and the `quantstrat`, `TTR`, and `quantmod` packages are loaded into your workspace.

```{r}
# Declare the DVO function
DVO <- function(HLC, navg = 2, percentlookback = 126) {
  
  # Compute the ratio between closing prices to the average of high and low
  ratio <- Cl(HLC)/((Hi(HLC) + Lo(HLC))/2)
  
  # Smooth out the ratio outputs using a moving average
  avgratio <- SMA(ratio, n = navg)
  
  # Convert ratio into a 0-100 value using runPercentRank()
  out <- runPercentRank(avgratio, n = percentlookback, exact.multiplier = 1) * 100
  colnames(out) <- "DVO"
  return(out)
}
```

# Apply and test Indicator

```{r}
# Add the DVO indicator to your strategy
add.indicator(strategy = strategy.st, name = "DVO",
              arguments = list(HLC = quote(HLC(mktdata)), navg = 2, percentlookback = 126),
              label = "DVO_2_126")

# Use applyIndicators to test out your indicators
test <- applyIndicators(strategy = strategy.st, mktdata = BTC_USD)

# Subset your data
test_subset <- test["2020-09-01/2020-09-05"]
```

# **Using sigComparison**

A **sigComparison** signal is a simple and useful way to compare two (hopefully related) quantities, such as two moving averages. Often, a sigComparison signal does not create a buy or sell signal by itself (as such a signal would involve buying or selling on every such day), but is most often useful as a filter for when another buy or sell rule should be followed.

In this exercise, you will use [**sigComparison()**](http://www.rdocumentation.org/packages/quantstrat/versions/0.8.2/topics/sigComparison) to generate a signal comparison that specifies that the 50-day simple moving average (SMA) must be above the 200-day simple moving average (SMA). You will label this signal `longfilter`, because it signals that the short-term average is above the long-term average.

```{r}
# Add a sigComparison which specifies that SMA50 must be greater than SMA200, call it longfilter
add.signal(strategy.st, name = "sigComparison", 
           
  # We are interested in the relationship between the SMA50 and the SMA200
  arguments = list(columns = c("SMA50", "SMA200"), 
                            
  # Particularly, we are interested when the SMA50 is greater than the SMA200
  relationship = "gt"),
           
  # Label this signal longfilter
  label = "longfilter")
```

# **Using sigCrossover**

While having a long filter is necessary, it is not sufficient to put on a trade for this strategy. However, the moment the condition does not hold, the strategy should not hold any position whatsoever. For this exercise, you will implement the opposite of the rule specified above using the `sigCrossover()` function.

As opposed to `sigComparison()`, which will always state whether or not a condition holds, `sigCrossover()` only gives a positive the moment the signal *first* occurs, and then not again. This is useful for a signal that will be used to initiate a transaction, as you only want one transaction in most cases, rather than having transactions fire again and again.

In this case, you will implement the [**sigCrossover()**](http://www.rdocumentation.org/packages/quantstrat/versions/0.8.2/topics/sigCrossover) function specifying that the `SMA50` crosses under the `SMA200`. You will label this signal `filterexit`, as it will exit your position when the moving average filter states that the environment is not conducive for the strategy to hold a position.

```{r}
# Add a sigCrossover which specifies that the SMA50 is less than the SMA200 and label it filterexit
add.signal(strategy.st, name = "sigCrossover",
           
  # We're interested in the relationship between the SMA50 and the SMA200
  arguments = list(columns = c("SMA50", "SMA200"),
                            
  # The relationship is that the SMA50 crosses under the SMA200
  relationship = "lt"),
           
  # Label it filterexit
  label = "filterexit")
```

# **Using sigThreshold - I**

In the next two exercises, you will focus on the `sigThreshold` signal. The sigThreshold signal is mainly used for comparing an indicator to a fixed number, which usually has applications for bounded oscillators, or perhaps rolling statistical scores (for example, for a trading strategy that might choose to go long when a ratio of mean to standard deviation is at -2, or vice versa). Whereas sigComparison and sigCrossover deal with quantities that are usually based off of an indicator that takes values in the same general area as prices, sigThreshold exists specifically to cover those situations outside the bounds of indicators that take values similar to prices.

Furthermore, the [**sigThreshold()**](http://www.rdocumentation.org/packages/quantstrat/versions/0.8.2/topics/sigThreshold) function takes the `cross` argument, which specifies whether it will function similarly to sigComparison (`cross = FALSE`) or sigCrossover (`cross = TRUE`), respectively. In this exercise, you will implement a variant of sigThreshold that functions similarly to sigComparison.

Your job will be to implement a sigThreshold that checks whether or not `DVO_2_126` is under 20. This signal will serve as one of the two switches that need to be "on" in order to enter into a long position in the strategy.

```{r}
# Implement a sigThreshold which specifies that DVO_2_126 must be less than 20, label it longthreshold
add.signal(strategy.st, name = "sigThreshold", 
           
 # Use the DVO_2_126 column
 arguments = list(column = "DVO_2_126", 
                            
 # The threshold is 20
 threshold = 20, 
                            
 # We want the oscillator to be under this value
 relationship = "lt", 
                            
 # We're interested in every instance that the oscillator is less than 20
 cross = FALSE), 
           
 # Label it longthreshold
 label = "longthreshold")
```

# **Using sigThreshold() - II**

In this exercise, you will implement a signal to exit a position given a certain threshold value of the `DVO`. While there are two entry signals that are both necessary but neither sufficient on its own, the two exit signals (this one and the one you implemented in an earlier exercise) are both sufficient on their own (but neither necessary in the existence of the other) to exit a position.

In this exercise, you will again use `sigThreshold()`, this time counting when the `DVO_2_126` crosses above a threshold of 80. To mimic a sigCrossover signal, set `cross` equal to `TRUE` Label this signal `thresholdexit`.

```{r}
# Add a sigThreshold signal to your strategy that specifies that DVO_2_126 must cross above 80 and label it thresholdexit
add.signal(strategy.st, name = "sigThreshold", 
           
   # Reference the column of DVO_2_126
   arguments = list(column = "DVO_2_126", 
                            
  # Set a threshold of 80
  threshold = 80, 
  
  # The oscillator must be greater than 80
  relationship = "gt", 
  
  # We are interested only in the cross
  cross = TRUE), 
           
 # Label it thresholdexit
 label = "thresholdexit")
```

# **Using sigFormula()**

The last signal function is a bit more open-ended. The [**sigFormula()**](http://www.rdocumentation.org/packages/quantstrat/versions/0.8.2/topics/sigFormula) function uses string evaluation to offer immense flexibility in combining various indicators and signals you already added to your strategy in order to create composite signals. While such catch-all functionality may seem complicated at first, with proper signal implementation and labeling, a `sigFormula` signal turns out to be the simplest of logical programming statements encapsulated in some quantstrat syntactical structuring.

In this exercise, you will get a taste of what the `sigFormula` function can do by stepping through the logic manually. You will need to use the [**applyIndicators()**](http://www.rdocumentation.org/packages/quantstrat/versions/0.8.2/topics/applyIndicators) and [**applySignals()**](http://www.rdocumentation.org/packages/quantstrat/versions/0.8.2/topics/applySignals) functions.

```{r}
# Create your dataset: test
test_init <- applyIndicators(strategy.st, mktdata = OHLC(BTC_USD))
test <- applySignals(strategy = strategy.st, mktdata = test_init)
```

# **Combining signals - II**

In the previous exercise, you approximated a `sigFormula` signal by comparing the value of two other signals. In this final exercise, you will take this one step futher by using the `sigFormula()` function to generate a sigFormula signal.

The goal of this exercise is simple. You want to enter into a position when both `longfilter` and `longthreshold` become true at the same time. The idea is this: You don't want to keep entering into a position for as long as conditions hold true, but you *do* want to hold a position when there's a pullback in an uptrending environment.

Writing a `sigFormula` function is as simple as writing the argument of an "if statement" in base R inside the `formula()` function. In this case, you want to create a signal labeled `longentry`, which is true when both `longfilter` and `longthreshold` cross over to true at the same time.

Once you complete this exercise, you will have a complete survey of how signals work in quantstrat!

```{r}
# Add a sigFormula signal to your code specifying that both longfilter and longthreshold must be TRUE, label it longentry
add.signal(strategy.st, name = "sigFormula",
           
   # Specify that longfilter and longthreshold must be TRUE
   arguments = list(formula = "longfilter & longthreshold", 
                    
                    # Specify that cross must be TRUE
                    cross = TRUE),
   
   # Label it longentry
   label = "longentry")
```

# **Using add.rule() to implement an exit rule**

Welcome to the chapter on rules! While rules in quantstrat can become very complex, this chapter will fill in many of the details for you to help you develop an understanding of the actual mechanics of rules. Rules are the final mechanic in the trinity of quantstrat mechanics -- indicators, signals, and rules. Rules are a way for you to specify exactly *how* you will shape your transaction once you decide you wish to execute on a signal.

Throughout this chapter, you will continue working the strategy developed in earlier chapters (`strategy.st`). Given that there are three rules to the strategy (two exit rules and one entry rule), there will be a handful of exercises to build up some intuition of the mechanics of rules.

This exercise will introduce you to the [**add.rule()**](http://www.rdocumentation.org/packages/quantstrat/versions/0.8.2/topics/add.rule) function, which allows you to add customized rules to your strategy.

```{r}
# Fill in the rule's type as exit
add.rule(strategy.st, name = "ruleSignal", 
         arguments = list(sigcol = "filterexit", sigval = TRUE, orderqty = "all", 
                        ordertype = "market", orderside = "long", 
                        replace = FALSE, prefer = "Open"), 
         type = "exit")
 
```

# **Specifying sigcol in add.rule()**

Great job! Although the `add.rule()` command looks complex, each argument is quite simple. To understand this command, you will explore each argument individually.

First, `add.rule()` takes the argument `sigcol`, which specifies the signal column in your strategy. Like signals and indicators, all rules reference a column already present in your strategy. Rules relies on signals, and must therefore reference the signal columns in your strategy.

In this exercise, you will supply the `add.rule()` call with the `sigcol` value, which will be set to `filterexit` (to reference the `filterexit` signal you created in the previous chapter). Specifically, the `filterexit` signal refers to the condition that the 50 day SMA has crossed under the 200 day SMA in your strategy. By creating a rule for this signal, you will be indicating that you wish to exit in this condition, as the market environment is no longer conducive to your position.

```{r}
# Fill in the sigcol argument in add.rule()
add.rule(strategy.st, name = "ruleSignal", 
         arguments = list(sigcol = "filterexit", sigval = TRUE, orderqty = "all", 
                        ordertype = "market", orderside = "long", 
                        replace = FALSE, prefer = "Open"), 
         type = "exit")
```

# **Specifying sigval in add.rule()**

Now that you've specified the column containing the relevant signal in your strategy, the next argument to specify in `add.rule()` is `sigval`, or the value that your signal should take to trigger the rule.

Remember that all signal outputs are either 1s or 0s. Effectively, a signal is either "on" or "off" at any given time. For our purposes, this is equivalent to two possible logical values: `TRUE` or `FALSE`. When specifying `sigval` in your `add.rule()` command, you need to indicate whether the rule is triggered when the signal value is `TRUE` or `FALSE`.

To proceed with the new exit rule in your strategy, you will want to specify that a transaction should occcur when `filterexit` is equal to `TRUE`.

```{r}
# Fill in the sigval argument in add.rule()
add.rule(strategy.st, name = "ruleSignal", 
         arguments = list(sigcol = "filterexit", sigval = TRUE, orderqty = "all", 
                        ordertype = "market", orderside = "long", 
                        replace = FALSE, prefer = "Open"), 
         type = "exit")
```

# **Specifying orderqty in add.rule()**

Now that you have a grasp of the first set of arguments in the `add.rule()` function, it's time to move on to the more important arguments: the actual order being bought or sold! The `orderqty` argument in the `ruleSignal` specifies exactly how much of an asset you want to buy or sell, in numbers of shares.

However, one salient feature of the `exit` rule type is that you can reduce your position to zero instantly with the `all` argument (hence, exiting). This is the mechanism we will implement in this exercise.

```{r}
# Fill in the orderqty argument in add.rule()
add.rule(strategy.st, name = "ruleSignal", 
         arguments = list(sigcol = "filterexit", sigval = TRUE, orderqty = "all", 
                        ordertype = "market", orderside = "long", 
                        replace = FALSE, prefer = "Open"), 
         type = "exit")
```

# **Specifying ordertype in add.rule()**

To this point you've specified the signal column, signal value, and order quantity associated with your rule. Next you will specify the type of order you will execute (`ordertype`).

While there are multiple types of orders in quantstrat, for the scope of this course you will stick to **market orders** (`ordertype = "market"`). A market order is an order that states that you will buy or sell the asset at the prevailing price, regardless of the conditions in the market. An alternative type of orders is a **limit order**, which specifies that the transaction will only take place if certain price conditions are met (namely, if the price falls below a certain further threshold on the day of the order). The mechanics of limit orders are outside the scope of this course.

```{r}
# Fill in the ordertype argument in add.rule()
add.rule(strategy.st, name = "ruleSignal", 
         arguments = list(sigcol = "filterexit", sigval = TRUE, orderqty = "all", 
                        ordertype = "market", orderside = "long", 
                        replace = FALSE, prefer = "Open"), 
         type = "exit")
```

# **Specifying orderside in add.rule()**

The next critical argument to specify in your order is `orderside`, which can take two values: either `long` or `short`. In quantstrat, long and short side trades are siloed off separately so that quantstrat knows whether a trade is a long trade or a short trade. A long trade is one that profits by buying an asset in the hopes that the asset's price will rise. A short trade is one that sells an asset before owning it, hoping to buy it back later at a lower price.

For your strategy, you will want to take only **long orders**.

```{r}
# Fill in the orderside argument in add.rule()
add.rule(strategy.st, name = "ruleSignal", 
         arguments = list(sigcol = "filterexit", sigval = TRUE, orderqty = "all", 
                        ordertype = "market", orderside = "long", 
                        replace = FALSE, prefer = "Open"), 
         type = "exit")
```

# **Specifying replace in add.rule()**

In quantstrat, the replace argument specifies whether or not to ignore all other signals on the same date when the strategy acts upon one signal. This is generally not a desired quality in a well-crafted trading system. Therefore, for your exit rule, you should set `replace` to `FALSE`.

Furthermore, you will be working with a new rule. Previously, the exit rule you worked with was when the market environment was no longer conducive to a trade. In this case, you will be working with a rule that sells when the DVO has crossed a certain threshold. In particular, you will be working with the `thresholdexit` rule now.

```{r}
# Fill in the replace argument in add.rule()
add.rule(strategy.st, name = "ruleSignal", 
         arguments = list(sigcol = "thresholdexit", sigval = TRUE, orderqty = "all", 
                        ordertype = "market", orderside = "long", 
                        replace = FALSE, prefer = "Open"), 
         type = "exit")
```

# **Specifying prefer in add.rule()**

Lastly, of the basic rule arguments, there is the aspect of the prefer argument. In quantstrat, orders have a "next-bar" mechanism. That is, if you would gain a signal on Tuesday, the earliest that a position would actually fulfil itself would be on the Wednesday after. However, this can be solved by placing orders to execute on the next possible opening price, rather than wait for an entire day to pass before being able to actually purchase/sell the asset.

```{r}
# Fill in the prefer argument in add.rule()
add.rule(strategy.st, name = "ruleSignal", 
         arguments = list(sigcol = "thresholdexit", sigval = TRUE, orderqty = "all", 
                        ordertype = "market", orderside = "long", 
                        replace = FALSE, prefer = "Open"), 
         type = "exit")
```

# **Using add.rule() to implement an entry rule**

Excellent! You've mastered every element of the rule building process in `quantstrat`. While thus far you've added rules step-by-step, now it's time to put it all together and see how well you've been able to absorb the material in this chapter.

The opposite of an exit rule is an **enter rule**. On enter rules, `orderqty` cannot be set to `"all"` because there is no initial position on which to act. In this exercise, you will implement an enter rule that references the `longentry` signal in your strategy and will buy one share of an asset.

```{r}
# Create an entry rule of 1 share when all conditions line up to enter into a position
add.rule(strategy.st, name = "ruleSignal", 
         
         # Use the longentry column as the sigcol
         arguments=list(sigcol = "longentry", 
                        
                        # Set sigval to TRUE
                        sigval = TRUE, 
                        
                        # Set orderqty to 1
                        orderqty = 1,
                        
                        # Use a market type of order
                        ordertype = "market",
                        
                        # Take the long orderside
                        orderside = "long",
                        
                        # Do not replace other signals
                        replace = FALSE, 
                        
                        # Buy at the next day's opening price
                        prefer = "Open"),
         
         # This is an enter type rule, not an exit
         type = "enter")

```

# **Running your strategy**

Congratulations on creating a strategy in `quantstrat`! To review, your strategy uses three separate indicators and five separate signals. The strategy requires both the threshold of the `DVO_2_126` indicator to be under 20 *and* the `SMA50` to be greater than the `SMA200`. The strategy sells when the `DVO_2_126` crosses above 80, or the `SMA50` crosses under the `SMA200`.

For this strategy to work properly, you specified five separate signals:

1.  `sigComparison` for `SMA50` being greater than `SMA200`;

2.  `sigThreshold` with `cross` set to `FALSE` for `DVO_2_126` less than 20;

3.  `sigFormula` to tie them together and set `cross` to `TRUE`;

4.  `sigCrossover` with `SMA50` less than `SMA200`; and

5.  `sigThreshold` with `cross` set to `TRUE` for `DVO_2_126` greater than 80.

The strategy invests \$100,000 (your `initeq`) into each trade, and may have some small dollar cost averaging if the `DVO_2_126` oscillates around 20 (though the effect is mostly negligible compared to the initial allocation).

In this final chapter, you will learn how to view the actual results of your portfolio. But first, in order to generate the results, you need to run your strategy and fill in some more boilerplate code to make sure `quantstrat` records everything. The code in this exercise is code you will have to copy and paste in the future.

```{r}
# Use applyStrategy() to apply your strategy. Save this to out
out <- applyStrategy(strategy = strategy.st, portfolios = portfolio.st)

# Update your portfolio (portfolio.st)
updatePortf(portfolio.st)
daterange <- time(getPortfolio(portfolio.st)$summary)[-1]

# Update your account (account.st)
updateAcct(account.st, daterange)
updateEndEq(account.st)
```

# **Profit factor**

One of the most vital statistics of any systematic trading strategy is the **profit factor**. The profit factor is how many dollars you make for each dollar you lose. A profit factor above 1 means your strategy is profitable. A profit factor below 1 means you should head back to the drawing board.

In this exercise, you will explore the profit factor in your strategy by creating an object called `tstats` that displays the trade statistics for your system. In general, trade statistics are generated by using the `tradeStats()` command.

```{r}
# Get the tradeStats for your portfolio
tstats <- tradeStats(Portfolios = portfolio.st)

# Print the profit factor
print(tstats$Profit.Factor)

```

# **Using chart.Posn()**

One of the most enlightening things about a trading system is exploring what positions it took over the course of the trading simulation, as well as *when* it had its profits and drawdowns. Looking at a picture of the performance can deliver a great deal of insight in terms of refining similar trading systems in the future.

In this exercise, you will use the `chart.Posn()` function. This generates a crisp and informative visualization of the performance of your trading system over the course of the simulation.

Your portfolio strategy (`portfolio.st`) is preloaded into your environment.

```{r}
# Use chart.Posn to view your system's performance on SPY
chart.Posn(Portfolio = portfolio.st, Symbol = "BTC-USD")

```

# **Adding an indicator to a chart.Posn() chart**

One of the more interesting things you can do with the `chart.Posn()` function is to superimpose indicators on top of it. This can help show what the strategy has actually been doing and why. However, in order to do this, you will need to recalculate the indicators outside the scope of your strategy. Once this is done, you simply add them to the `chart.Posn` plot.

In this exercise, you will add the three indicators from your strategy to the `chart.Posn` plot you just created. The two moving averages (`SMA50` and `SMA200`) will be superimposed on the price series, while the `DVO_2_126` will have its own window.

```{r}
# Compute the SMA50
sma50 <- SMA(x = Cl(SPY), n = 50)

# Compute the SMA200
sma200 <- SMA(x = Cl(SPY), n = 200)

# Compute the DVO_2_126 with an navg of 2 and a percentlookback of 126
dvo <- DVO(HLC = HLC(SPY), navg = 2, percentlookback = 126)

# Recreate the chart.Posn of the strategy from the previous exercise
chart.Posn(Portfolio = portfolio.st, Symbol = "SPY")

# Overlay the SMA50 on your plot as a blue line
add_TA(sma50, on = 1, col = "blue")

# Overlay the SMA200 on your plot as a red line
add_TA(sma200, on = 1, col = "red")

# Add the DVO_2_126 to the plot in a new window
add_TA(dvo)
```

# **Cash Sharpe ratio**

When working with cash profit and loss statistics, quantstrat offers a way to compute a Sharpe ratio not just from returns, but from the actual profit and loss statistics themselves. A **Sharpe ratio** is a metric that compares the average reward to the average risk taken. Generally, a Sharpe ratio above 1 is a marker of a strong strategy.

In this exercise, you will see that because of trading P&L (profit and loss), one can compute a Sharpe ratio based on these metrics. The code below can be used to compute the Sharpe ratio based off of P&L. Copy the code in the console. In what range is the Sharpe ratio you obtain?

    portpl <- .blotter$portfolio.firststrat$summary$Net.Trading.PL
    SharpeRatio.annualized(portpl, geometric=FALSE)

```{r}portpl <- .blotter$portfolio.firststrat$summary$Net.Trading.PL}
SharpeRatio.annualized(portpl, geometric=FALSE)

```

# **Returns Sharpe ratio in quantstrat**

One of the main reasons to include an initial equity (in this case, `initeq`, which is set to 100,000) in your strategy is to be able to work with returns, which are based off of your profit and loss over your initial equity.

While you just computed a *cash* Sharpe ratio in the previous exercise, you will see in this exercise that quantstrat can also compute the standard *returns-based* Sharpe ratio as well.

```{r}
# Get instrument returns
instrets <- PortfReturns(portfolio.st)

# Compute Sharpe ratio from returns
SharpeRatio.annualized(instrets, geometric = FALSE)
```
