---
title: "Setup and Play with Quantstrat"
output:
  html_document: default
  pdf_document: default
---

Based on the Course [Financial Trading in R](https://learn.datacamp.com/courses/financial-trading-in-r)

# Setup

```{r setup, include=FALSE}
pacman::p_load(remotes, devtools)
#remotes::install_github("braverock/blotter")
#remotes::install_github("braverock/quantstrat")
pacman::p_load(quantmod, quantstrat, TTR)
```

## Two trading philosophies

-   Trend trading (also divergence or momentum), which is a bet that a quantity, such as a price, will keep moving in its current direction.
-   Reversion trading (also convergence, cycle, or oscillation), which is a bet that a quantity, such as a price, will reverse.

## How to prevent overfitting

-   Examining the robustness of system performance.
-   Reducing the number of parameters in the trading system.
-   Conducting tests to determine statistical significance of a strategy.

# Getting Bitcoin data

```{r}
# Get Bitcoin price from yahoo
getSymbols("BTC-USD",
           from = "2015-01-01", 
           to = "2020-12-31", 
           src = "yahoo", 
           adjust =  TRUE)

BTC_USD <- na.exclude(`BTC-USD`, 0)

# Plot the closing price of BTC
plot(Cl(BTC_USD))

# Adding moving average
lines(SMA(Cl(BTC_USD), n = 200), col = "red")
```

# Setting up a Strategy

### Understanding initialization settings

Let's get started with creating our first strategy in `quantstrat`. In this exercise, you will need to fill in three dates:

1.  An initialization date for your backtest.

2.  The start of your data.

3.  The end of your data.

```{r}
# Load the quantstrat package
library(quantstrat)

# Create initdate, from, and to strings
initdate <- "1999-01-01"
from <- "2000-01-01"
to <- "2021-02-28"

# Set the timezone to UTC
Sys.setenv(TZ = "UTC")

# Set the currency to USD 
currency("USD")
```

Let's continue the setup of your strategy. First, you will set a trade size of 100,000 USD in an object called `tradesize`
which determines the amount you wager on each trade. Second, you will
set your initial equity to 100,000 USD in an object called `initeq`.

Quantstrat requires three different objects to work: an **account**, a **portfolio**, and a **strategy**.
An account is comprised of portfolios, and a portfolio is comprised of
strategies. For your first strategy, there will only be one account, one
portfolio, and one strategy. Let's call them `"firststrat"` for "first strategy".

Finally, before proceeding, you must remove any existing strategies using the strategy removal command `rm.strat()` which takes in a string of the name of a strategy.

```{r}
# Define your trade size and initial equity
tradesize <- 100000
initeq <- 100000

# Define the names of your strategy, portfolio and account
strategy.st <- "firststrat"
portfolio.st <- "firststrat"
account.st <- "firststrat"

# Remove the existing strategy if it exists
rm.strat(strategy.st)
```

Now that everything has been named, you must initialize the portfolio, the account, the **orders**, and the strategy to produce results.

-   The portfolio initialization `initPortf()` needs a portfolio string `name`, a vector for `symbols` used in the backtest, an initialization date `initDate`, and a `currency`.

-   The account initialization call `initAcct()` is identical to the portfolio initialization call except it takes an account string `name` instead of a new portfolio name, an existing `portfolios` name, and an initial equity `initEq`.

-   The orders initialization `initOrders()` needs a portfolio string `portfolio` and an initialization date `initDate`.

-   The strategy initialization `strategy()` needs a `name` of this new strategy and must have `store` set to `TRUE`.

```{r}
# Initialize the portfolio
initPortf(portfolio.st, symbols = "BTC-USD", initDate = initdate, currency = "USD")

# Initialize the account
initAcct(account.st, portfolios = portfolio.st, initDate = initdate, currency = "USD", initEq = initeq)

# Initialize the orders
initOrders(portfolio.st, initDate = initdate)

# Store the strategy
strategy(strategy.st, store = TRUE)
```

# Indicators

Indicators are crucial for your trading strategy. They are transformations of market data that allow a clearer understanding of its overall behavior, usually in exchange for lagging the market behavior.
Here, you will be working with both trend types of indicators as well as oscillation indicators. You will also learn how to use pre-programmed indicators available in other libraries as well as implement one of your own.

The SMA and RSI functions

The **simple moving average (SMA)** and **relative strength index (RSI)**
are two classic indicators. As you saw in Chapter 1, the SMA is an arithmetic moving average of past prices, while the RSI is a bounded oscillating indicator that ranges from 0 to 100. Their respective functions `SMA()` and `RSI()` both take in a series of prices, denoted by `x` and `price` respectively, and a lookback period `n`, for example:

```{r}
# Create a 200-day SMA
spy_sma <- SMA(x = Cl(BTC_USD), n = 200)

# Create an RSI with a 3-day lookback period
spy_rsi <- RSI(price = Cl(BTC_USD), n = 3)
```

```{r}
# Plot the closing prices of BTC_USD
plot(Cl(BTC_USD))

# Overlay a 200-day SMA
lines(SMA(Cl(BTC_USD), n = 200), col = "red")

# What kind of indicator?
# trend
```

The [Relative Strength Index (RSI)](http://www.investopedia.com/terms/r/rsi.asp)
is another indicator that rises with positive price changes and falls with negative price changes. It is equal to 100 - 100/(1 + RS), where RS is the average gain over average loss over the lookback period. At various lengths, this indicator can range from a reversion indicator, to a trend filter, or anywhere in between. There are various ways of
computing the RSI.

```{r}
# Plot the closing price of BTC_USD
plot(Cl(BTC_USD))

# Plot the RSI 2
plot(RSI(Cl(BTC_USD), n = 2))

# What kind of indicator?
# print("reversion")
```

# Adding an Indicator

```{r}
# Add a 200-day SMA indicator to strategy.st
add.indicator(strategy = strategy.st, 
              
              # Add the SMA function
              name = "SMA", 
              
              # Create a lookback period
              arguments = list(x = quote(Cl(BTC_USD)), n = 200), 
              
              # Label your indicator SMA200
              label = "SMA200")
```

```{r}
# Add a 50-day SMA indicator to strategy.st
add.indicator(strategy = strategy.st, 
              
              # Add the SMA function
              name = "SMA", 
              
              # Create a lookback period
              arguments = list(x = quote(Cl(BTC_USD)), n = 50), 
              
              # Label your indicator SMA50
              label = "SMA50")
```

```{r}
# Add an RSI 3 indicator to strategy.st
add.indicator(strategy = strategy.st, 
              
              # Add the RSI 3 function
              name = "RSI", 
              
              # Create a lookback period
              arguments = list(price = quote(Cl(BTC_USD)), n = 3), 
              
              # Label your indicator RSI_3
              label = "RSI_3")
```

# Writing our own Indicators

```{r}
# Write the calc_RSI_avg function
calc_RSI_avg <- function(price, n1, n2) {
  
  # RSI 1 takes an input of the price and n1
  RSI_1 <- RSI(price = price, n = n1)
  
  # RSI 2 takes an input of the price and n2
  RSI_2 <- RSI(price = price, n = n2)
  
  # RSI_avg is the average of RSI_1 and RSI_2
  RSI_avg <- (RSI_1 + RSI_2)/2
  
  # Your output of RSI_avg needs a column name of RSI_avg
  colnames(RSI_avg) <- "RSI_avg"
  return(RSI_avg)
}

# Add this function as RSI_3_4 to your strategy with n1 = 3 and n2 = 4
add.indicator(strategy.st, name = "calc_RSI_avg", arguments = list(price = quote(Cl(BTC_USD)), n1 = 3, n2 = 4), label = "RSI_3_4")

# Use applyIndicators to test out your indicators
test <- applyIndicators(strategy = strategy.st, mktdata = BTC_USD)

# Subset your data
test_subset <- test["2020-09-01/2020-09-05"]
```

While the RSI is decent, it is somewhat outdated as far as indicators go. In this exercise, you will code a simplified version of another indicator from scratch. The indicator is called the **David Varadi Oscillator (DVO)**, originated by David Varadi, a quantitative research director.

The purpose of this oscillator is similar to something like the RSI in that it attempts to find opportunities to buy a temporary dip and sell in a temporary uptrend. In addition to obligatory market data, an oscillator function takes in two lookback periods.

First, the function computes a ratio between the closing price and average of high and low prices. Next, it applies an SMA to that quantity to smooth out noise, usually on a very small time frame, such as two days. Finally, it uses the [runPercentRank()](http://www.rdocumentation.org/packages/TTR/versions/0.23-1/topics/runPercentRank) function to take a running percentage rank of this average ratio, and multiplies it by 100 to convert it to a 0-100 quantity.

Think about the way that students get percentile scores after taking a standardized test (that is, if a student got an 800 on her math section, she might be in the 95th percentile nationally). `runPercentRank()`
does the same thing, except over time. This indicator provides the rank for the latest observation when taken in the context over some past period that the user specifies. For example, if something has a
runPercentRank value of .90 when using a lookback period of 126, it means it's in the 90th percentile when compared to itself and the past 125 observations.

Your job is to implement this indicator and save it as `DVO`. Some of the necessary code has been provided, and the `quantstrat`, `TTR`, and `quantmod` packages are loaded into your workspace.

```{r}
# Declare the DVO function
DVO <- function(HLC, navg = 2, percentlookback = 126) {
  
  # Compute the ratio between closing prices to the average of high and low
  ratio <- Cl(HLC)/((Hi(HLC) + Lo(HLC))/2)
  
  # Smooth out the ratio outputs using a moving average
  avgratio <- SMA(ratio, n = navg)
  
  # Convert ratio into a 0-100 value using runPercentRank()
  out <- runPercentRank(avgratio, n = percentlookback, exact.multiplier = 1) * 100
  colnames(out) <- "DVO"
  return(out)
}
```

# Apply and test Indicator

```{r}
# Add the DVO indicator to your strategy
add.indicator(strategy = strategy.st, name = "DVO",
              arguments = list(HLC = quote(HLC(mktdata)), navg = 2, percentlookback = 126),
              label = "DVO_2_126")

# Use applyIndicators to test out your indicators
test <- applyIndicators(strategy = strategy.st, mktdata = BTC_USD)

# Subset your data
test_subset <- test["2020-09-01/2020-09-05"]
```
```{r}

```


